---
title: "R Markdown test rmd"
author: '*Compiled on `r date()` by `r Sys.info()["user"]`*'
output:
  html_document:
    highlight: haddock
    includes:
      in_header: ~/github/ohibc/src/templates/ohibc_hdr1.html
    number_sections: yes
    theme: cerulean
    toc: yes
  html_notebook: null
  pdf_document:
    toc: yes
---

-----

```{r setup, echo = TRUE, message = FALSE, warning = FALSE}
dir_git <- '~/github/provRmd'
library(dplyr)
library(readr)
library(stringr)

dir_test <- file.path(dir_git, 'rmd_testing')

### set up provenance tracking for this script:
# document(); install()
library(provRmd)
prov_setup()### initializes prov_track and loads functions

```

# read a table; capture prov info

```{r read global species list, echo = TRUE, message = FALSE, warning = FALSE}
table1_file <- file.path(dir_test, 'table1.csv')
table1      <- read.csv(table1_file, stringsAsFactors = FALSE)

table2_file <- file.path(dir_test, 'table2.csv')
write.csv(table1, table2_file)

table3_file <- file.path(dir_test, 'table3.csv')
write.csv(table1, table3_file)

```

```{r sourcing a file, message = FALSE, echo = TRUE}
source(file.path(dir_test, 'test_source.R'))

```

```{r display table, echo = TRUE}
DT::datatable(table1,   ### does not display system and session info
              caption  = 'this is a sample table:',              
              rownames = FALSE,
              class    = 'stripe hover compact',
              options  = list(dom = 'tp'))
```

-----

# The next section (below the divider) is the footer, knitted as a child

The code for the R footer looks like this:

`prov_wrapup()`

Note that it needs to be included in a code chunk with option `results = 'asis'` in order for all the text to display properly.  The code generates Markdown, which is executed as if it were just part of this main document; it numbers the section ("Provenance") as a continuation of the numbering, and the variables are evaluated in the environment of the main document.

``` {r, message = FALSE, results = 'asis'}

# nodes <- read_csv('~/github/provRmd/rmd_testing/nodes.csv')
# edges <- read_csv('~/github/provRmd/rmd_testing/edges.csv')
prov_wrapup()

```
